Von Neumann-Morgenstern and Savage Theorems for Causal Decision Making

### 2020-09-15 Artificial_Intelligence_Journal/Draft/AIJ_Draft.tex
cambios de redaccion en main result

\subsection{Main Result}
In this work we extend Pearl's result to the case where a decision maker \textit{does not know the causal mechanism} that controls her environment, so she holds \textit{beliefs} about possible causal models and uses such beliefs \textit{as if} they were true, as prescribed by \cite{joyce1999foundations}, in order to attempt to make a good choice given her beliefs. We provide an explicit way of choosing an optimal decision given what the decision maker believes about the causal structure of her environment, thus providing a causal version of Savage's Theorem. We take a normative point of view to study how causal relations \textit{should} be used by a rational agent when making decisions which have uncertain consequences.

>>>>

\subsection{Main Result}
In this work we extend a result from \cite{pearl2009causality} about decision making using known causal information to the case in which a decision maker \textit{does not know the causal mechanism} that controls her environment. In our result, the decision maker holds \textit{beliefs}, encoded as a probability distribution over possible causal models, and uses such beliefs \textit{as if} they were true, as prescribed by \cite{joyce1999foundations} and using Pearl's result, in order to attempt to make a good choice given her current beliefs. We provide an explicit way of choosing an optimal decision given what the decision maker believes about the causal structure of her environment, thus providing a causal version of Savage's Theorem. We take a normative point of view to study how causal relations \textit{should} be used by a rational agent when making decisions which have uncertain consequences.
